Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2015-01-27 Paper/ms.tex
% sign

The posterior distribution for the periods $\{P_i\}_{i=1}^N$ is shown in
Figure~\ref{fig:fake_data_periods}. Because of the label switching degeneracy,
the posterior distribution for each period is identical, so we pooled the
samples for all periods. Defining the log-periods by
$S_i =  \log_{10}\left[P_i/(\textnormal{1 day})\right]$,
Figure~\ref{fig:fake_data_periods} is a Monte Carlo representation
of the mixture distribution
\begin{eqnarray}
f(S) &=& \sum_{N=0}^{10} p(N | D)\sum_{i=1}^N p(S_i | N, D).
\end{eqnarray}
If a certain period is accurately measured (i.e. it appears in close to 100 of
the posterior samples and the distribution for its period is very narrow)
then it will appear in Figure 3 with a height of $\sim 520$. If the uncertainty
in the period is larger than the histogram bin width then the peak will be
spread over several bins.

>>>>

The posterior distribution for the periods $\{P_i\}_{i=1}^N$ is shown in
Figure~\ref{fig:fake_data_periods}. Because of the label switching degeneracy,
the posterior distribution for each period is identical, so we pooled the
samples for all periods. Defining the log-periods by
$S_i =  \log_{10}\left[P_i/(\textnormal{1 day})\right]$,
Figure~\ref{fig:fake_data_periods} is a Monte Carlo representation
of the mixture distribution
\begin{eqnarray}
f(S) &=& \sum_{N=0}^{10} p(N | D)\sum_{i=1}^N p(S_i | N, D).
\end{eqnarray}
If a certain period is accurately measured (i.e. it appears in close to 100\% of
the posterior samples and the distribution for its period is very narrow)
then it will appear in Figure 3 with a height of $\sim 520$. If the uncertainty
in the period is larger than the histogram bin width then the peak will be
spread over several bins.
